Automated iterative forecasting for the Portal Project

### 2018-01-20 manuscript/portal_iterative_forecasting_ms.Rmd
Add missing references.

---
title: "Automated iterative forecasting for the Portal Project"
csl: csl.csl
fontsize: 12pt
output:
  html_document: default
  pdf_document:
    keep_tex: yes
header-includes:
- \usepackage{times}
- \usepackage{setspace}
- \usepackage{booktabs}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
geometry: left=3.5cm, right=3.5cm, top=2.25cm, bottom=2.25cm, headheight=12pt, letterpaper
bibliography: refs.bib
---
\raggedright

@@

Publicly archiving forecasts before new data is collected allows the field to assess, compare, and build on forecasts made by different groups [@mcgill2012; @tredennick2016; @dietze2017; @harris2017]. This archiving serves as a form of pre-registration for model predictions, helping facilitate unbiased interpretation of model performance. We explored three major repositories for archiving our forecasts: FigShare, Zenodo, and Open Science Framework. While all three repositories allowed for easy manual submissions (i.e., a human uploading files after each forecast), automating this process was substantially more difficult. Various combinations of repositories, APIs and associated R packages had issues with: 1) integrating authorization with continuous integration; 2) automatically making archived files public; 3) adding new files to an existing location; or 4) automatically permanently archiving the files. Our eventual solution was to leverage the GitHub-Zenodo integration (https://guides.github.com/activities/citable-code/) and automatically push forecasts to the GitHub repository from the CI server. The GitHub-Zenodo integration is designed to automatically create versioned archives of GitHub repositories. There is an existing one-time process for linking our forecasting repository on  GitHub with Zenodo. Once this link is created, each time a new forecast is created, our pipeline adds the new forecasts to the GitHub repository and uses the GitHub API to create a new "release" of our repository. This triggers the Zenodo-GitHub integration, which automatically archives the resulting forecasts and the code that generated them under a top-level DOI that refers to all archived forecasts ([https://doi.org/10.5281/zenodo.833438](https://doi.org/10.5281/zenodo.833438)). Through this process, we automatically archive every forecast made with a documented history of the archive. While this approach is functional because everything in the repository is archived when a new forecast is made, these archives are complicated, making it more complicated than necessary to find and access the forecasting results.

@@

Because of the breadth of expertise needed to set up our forecasting pipeline, our effort required a team with diverse skills and perspectives, ranging from software development to field site expertise. It is rare to find such breadth within a single research group, and our system was developed as a collaboration between the lab collecting the data and a computational ecology lab. When teams have a breadth of expertise, communication can be challenging. We found a shared base of knowledge related to both the field research and fundamental computational skills was important for the success of the group. Everyone on the team had received training in fundamental data management and computing skills through a combination of university courses, Software and Data Carpentry workshops [@teal2016], and informal lab training efforts. In addition, everyone was broadly familiar with the study site and methods of data collection, and most team members had participated in field work at the site on multiple occasions. This provided a shared set of knowledge and vocabulary that actively facilitated interdisciplinary interactions. Given the current state of existing tools for forecasting, forecasting teams will need people with significant experience in working with continuous integration and APIs, which means interdisciplinary teams will generally be required for creating these pipelines until tool development improves.

>>>>

---
title: "Automated iterative forecasting for the Portal Project"
csl: csl.csl
fontsize: 12pt
output:
  pdf_document:
    keep_tex: yes
  html_document: default
header-includes:
- \usepackage{times}
- \usepackage{setspace}
- \usepackage{booktabs}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
geometry: left=3.5cm, right=3.5cm, top=2.25cm, bottom=2.25cm, headheight=12pt, letterpaper
bibliography: refs.bib
---
\raggedright

@@

Publicly archiving forecasts before new data is collected allows the field to assess, compare, and build on forecasts made by different groups [@mcgill2012; @tredennick2016; @dietze2017; @harris2018]. This archiving serves as a form of pre-registration for model predictions, helping facilitate unbiased interpretation of model performance. We explored three major repositories for archiving our forecasts: FigShare, Zenodo, and Open Science Framework. While all three repositories allowed for easy manual submissions (i.e., a human uploading files after each forecast), automating this process was substantially more difficult. Various combinations of repositories, APIs and associated R packages had issues with: 1) integrating authorization with continuous integration; 2) automatically making archived files public; 3) adding new files to an existing location; or 4) automatically permanently archiving the files. Our eventual solution was to leverage the GitHub-Zenodo integration (https://guides.github.com/activities/citable-code/) and automatically push forecasts to the GitHub repository from the CI server. The GitHub-Zenodo integration is designed to automatically create versioned archives of GitHub repositories. There is an existing one-time process for linking our forecasting repository on  GitHub with Zenodo. Once this link is created, each time a new forecast is created, our pipeline adds the new forecasts to the GitHub repository and uses the GitHub API to create a new "release" of our repository. This triggers the Zenodo-GitHub integration, which automatically archives the resulting forecasts and the code that generated them under a top-level DOI that refers to all archived forecasts ([https://doi.org/10.5281/zenodo.833438](https://doi.org/10.5281/zenodo.833438)). Through this process, we automatically archive every forecast made with a documented history of the archive. While this approach is functional because everything in the repository is archived when a new forecast is made, these archives are complicated, making it more complicated than necessary to find and access the forecasting results.

@@

Because of the breadth of expertise needed to set up our forecasting pipeline, our effort required a team with diverse skills and perspectives, ranging from software development to field site expertise. It is rare to find such breadth within a single research group, and our system was developed as a collaboration between the lab collecting the data and a computational ecology lab. When teams have a breadth of expertise, communication can be challenging. We found a shared base of knowledge related to both the field research and fundamental computational skills was important for the success of the group. Everyone on the team had received training in fundamental data management and computing skills through a combination of university courses, Software and Data Carpentry workshops [@teal2015], and informal lab training efforts. In addition, everyone was broadly familiar with the study site and methods of data collection, and most team members had participated in field work at the site on multiple occasions. This provided a shared set of knowledge and vocabulary that actively facilitated interdisciplinary interactions. Given the current state of existing tools for forecasting, forecasting teams will need people with significant experience in working with continuous integration and APIs, which means interdisciplinary teams will generally be required for creating these pipelines until tool development improves.
